---
title: "SLICED! S01E08 Analysis"
output: html_notebook
---

```{r, setup-options, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 5, fig.height = 8,
  warning = FALSE,
  cache = TRUE
)
```

# Packages
```{r}
library(tidyverse)
library(tidymodels)
library(magrittr)
```
# Read in the data
```{r}
raw_train <- read_csv("train.csv")
raw_test <- read_csv("test.csv")
raw_artists <- read_csv("artists.csv")
sample_sub <- read_csv("sample_submission.csv")
```
# Check out the data
```{r}
glimpse(raw_train)
```
```{r}
glimpse(raw_artists)
```
# Data dictionary

## tracks.csv
* id                (Unique identifier of track)
* name              (Name of the song)
* popularity        (Ranges from 0 to 100)
* duration_ms       (Integer typically ranging from 200k to 300k)
* artists           (List of artists mentioned)
* id_artists        (Ids of mentioned artists)
* danceability      (Ranges from 0 to 1)
* energy            (Ranges from 0 to 1)
* key               (All keys on octave encoded as values ranging from 0 to 11, starting on C as 0, C# as 1 and so on...)
* loudness          (Float typically ranging from -60 to 0)
* speechiness       (Ranges from 0 to 1)
* acousticness      (Ranges from 0 to 1)
* instrumentalness  (Ranges from 0 to 1)
* liveness          (Ranges from 0 to 1)
* valence           (Ranges from 0 to 1)
* tempo             (Float typically ranging from 50 to 150)
* release_year      (Year of release)
* release_month     (Month of year released)
* release_day       (Day of month released)

##artists.csv
* id (Id of artist)
* followers (Total number of followers of artist)
* genres (Genres associated with this artist)
* name (Name of artist)
* popularity (Popularity of given artist based on all his/her tracks)


# Tidy up the data using a recipe
```{r}
recipe <- recipe(popularity ~ ., data = raw_train) %>% 
  step_mutate()
```

# EDA
```{r}
raw_train %>% 
  # filter(popularity >= 50) %>% 
  ggplot(aes(y = valence, x = tempo, alpha = popularity)) +
  geom_point()
```

